DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
provided link to the documentation and videos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%---------------------------------------------------
\section{Counterexample-Guided Inductive Synthesis for Control Systems}
%---------------------------------------------------

@@

Our CEGIS engine is implemented as an integrated module within the C bounded model checker (CBMC)~\cite{cbmc}.  CBMC
transforms the ANSI-C representation of our closed-loop control system model into its internal format called
\emph{GOTO}.  We instrument this internal \emph{GOTO} program for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an underlying SAT or SMT solver to solve the
resulting formulae.  We model FWL effects, time discretization and the presence of quantization noise explicitly using CBMC's  
nondeterminism API (e.g., \texttt{nondet}, \texttt{CPROVER\_assume} intrinsic functions).  Our module was included in CBMC~5.7 and is available for
public download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}  We further created a VirtualBox OVA image
with our tool pre-installed, including our MATLAB-generated benchmarks and benchmark shell script with instructions
to run all benchmarks and reproduce our
experiments\.footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}  The current development branch
of our tool is available in a public GitHub
repository.\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}

The entire implementation consists of $400$ lines of MATLAB scripts for the UI
module, $585$ and $800$ lines of C code in the naive and abstract accelerator
model, respectively.  $4000$ lines of C code for utility functions such as
interval and fixed-point arithmetic, as well as $1000$ lines of C++ code in the
control synthesis module in CEGIS CBMC.  We evaluate \tool using about $20$ 
control system benchmarks.

>>>>

%---------------------------------------------------
\section{Counterexample-Guided Inductive Synthesis for Control Systems}
\label{sec:CEGIS}
%---------------------------------------------------

@@

Our CEGIS engine is implemented as an integrated module within the C bounded model checker (CBMC)~\cite{cbmc}.  CBMC
transforms the ANSI-C representation of our closed-loop control system model into its internal format called
\emph{GOTO}.  We instrument this internal \emph{GOTO} program for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an underlying SAT or SMT solver to solve the
resulting formulae.  We model FWL effects, time discretization and the presence of quantization noise explicitly using CBMC's  
nondeterminism API (e.g., \texttt{nondet}, \texttt{CPROVER\_assume} intrinsic functions).  Our module was included in CBMC~5.7 and is available for
public download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}  We further created a VirtualBox OVA image
with our tool pre-installed, including our MATLAB-generated benchmarks and benchmark shell script with instructions
to run all benchmarks and reproduce our
experiments.\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}  The current development branch
of our toolbox is available in a public GitHub
repository.\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}

The entire implementation consists of $400$ lines of MATLAB scripts for the UI
module, $585$ and $800$ lines of C code in the naive and abstract accelerator
back-ends, respectively (cf.~Section~\ref{sec:CEGIS}).  $4000$ lines of C code for utility functions such as
interval and fixed-point arithmetic, as well as $1000$ lines of C++ code in the
control synthesis module in CEGIS CBMC.  We evaluate \tool using about $20$ 
control system benchmarks. Additionally, the documentation and videos about \tool are available 
at \url{http://dsverifier.org/dsverifier/dssynth-toolbox/}.
